|

### 2021-02-14 appendix/appendix.Rmd
small changes to seeded lda model

Our last model is a semisupervised LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include words for
children, life, and victim (along with possible variations). The second topic
describes crime characteristics with words such as murder, rape, kill, molest,
and steal. The next group has four keywords that describe lynching
perpetrators, and they are gangs, family, bystanders, and police. The fourth
topic includes terms to identify respondents who are against lynchings, and we
added against, none, do not agree, and choice as the seed terms. We see that
these groups have a large number of terms each, and that crime characteristics
is the topic that shows more often when our terms are applied.

\footnotesize
```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
# Semisupervised LDA
keywords <- dictionary(list(Victim      = c("crian*", "vida*", "v*tima*"),
                            Crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
                            Perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
                            Against     = c("contra", "nenhum*", "n*o concord*", "op**o")))

>>>>

Our last model is a semisupervised LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include the
Portuguese words for _children_, _life_, and _victim_ (along with possible
variations). The second topic describes crime characteristics with words such
as _murder_, _rape_, _kill_, _molest_, and _steal_. The next group has four
keywords that describe lynching perpetrators, and they are _gangs_, _family_,
_bystanders_, and _police_. The fourth topic includes terms to identify
respondents who are against lynchings, and we added _against_, _none_, _do not
agree_, and _choice_ as the seed terms. We see that these groups have a large
number of terms each, and that crime characteristics is the topic that shows
more often when our terms are applied.

\footnotesize
```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
# Semisupervised LDA
keywords <- dictionary(list(victim      = c("crian*", "vida*", "v*tima*"),
                            crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
                            perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
                            against     = c("contra", "escolha", "nenhum*", "n*o concord*", "op**o")))
